Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-10-27 Thesis/chapter/060-results-material.tex
ir figures included

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{XRD}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra}
	\label{fig:xrd}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SEM}
\begin{figure}
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
        \caption{71 fto old 1x} \label{fig:sem-old1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
        \caption{71 fto old 2x} \label{fig:sem-old2}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
        \caption{115 fto cs 1x} \label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \caption{147 steel ph? 10x} \label{fig:sem-ph}
    \end{subfigure}
    \caption{sem}
    \label{fig:sem}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Material Scientific}
\subsubsection{First recipe} 
As already indicated in the experimental section the recipe adopted from \cite{Anwar2017} didn't produce any \td{good} results. 
The solution was milky/cloudy and didn't produce homogeneous films. 
Altering the composition, pH, surfactant etc. didn't improve the resulting layers. 
%- first recipe tried to improve to achieve more restisting layer. by pH value, surface tension and solution ratios (only 10\% change because it was assumed, that the recipe is good and should be improved, but the recipe should be altered thoroughly. two layers were also tried but didn't even pass the visual examination/test/inspection. A curst was produced.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Material Scientific}
\subsubsection{Solution}
As already indicated in the experimental section the recipe adopted from \cite{Anwar2017} didn't produce any \td{good} results. 
The solution was milky/cloudy and didn't produce homogeneous films. 
Altering the composition, pH, surfactant etc. didn't improve the resulting \gls{zro} layers. 
%- first recipe tried to improve to achieve more restisting layer. by pH value, surface tension and solution ratios (only 10\% change because it was assumed, that the recipe is good and should be improved, but the recipe should be altered thoroughly. two layers were also tried but didn't even pass the visual examination/test/inspection. A curst was produced.

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infra Red}

\begin{figure}
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
        \caption{Transmittance of \gls{zro} on glass} \label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
        \caption{reflectance of \gls{zro} on glass} \label{fig:ir-gr}
    \end{subfigure}
    \caption{IR} \label{fig:ir}
\end{figure}

In figure \ref{fig:ir-gt} transmission spectra of visible and \gls{nir} light can be seen. 
Each sample had different numbers of layers. 
The incident angle was 0 degree for each sample.
differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers the more of the light is absorbed (800nm) by the \gls{zro} layers. 
%The trend is not monotone due to 
The thicker the layer is the more wavy the graph, which can be most likely be attributed to interferrence. 
This trend can also be observed in figure \ref{fig:ir-gr}
Figure \ref{fig:ir-gr} shows reflectance spectra of visible and \gls{nir} at an angle of 45 degrees. 
%\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{SEM}
\begin{figure}
    \centering
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_1x.png}
        \caption{71 fto old 1x} \label{fig:sem-old1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/071_fto_old_2x.png}
        \caption{71 fto old 2x} \label{fig:sem-old2}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/115_fto_cs_1x.png}
        \caption{115 fto cs 1x} \label{fig:sem-cs1}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Pics/sem/147_steel_ph_10x.png}
        \caption{147 steel ph? 10x} \label{fig:sem-ph}
    \end{subfigure}
    \caption{sem}
    \label{fig:sem}
\end{figure}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{XRD}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra}
	\label{fig:xrd}
\end{figure}
